A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-12-21 paper/submission/theor-experiment.tex
removing grids from plots in figure 10

%\vspace{0.2cm}
\begin{samepage}
	\begin{Verbatim}[fontsize=\scriptsize]
	OPTION, ECHO=FALSE;
	OPTION, INFO=TRUE;

@@

	OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
	OUTPUT="optLinac_40nC",
	OUTDIR="results",
	OBJECTIVES = {rmss1, emitx1, rmss2, emitx2},
	DVARS = {dv0, dv1, dv2, dv3, dv4, dv5, dv6, dv7},
	CONSTRAINTS = {c1, c2},
	INITIALPOPULATION=80,
	MAXGENERATIONS=100,
	NUM_MASTERS=1,
	NUM_COWORKERS=8,
	SIMTMPDIR="tmp",
	TEMPLATEDIR="tmpl",
	\end{Verbatim}
\end{samepage}

%\vspace{0.2cm}

@@

\begin{figure}
	\centering
	\begin{minipage}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/ex-pareto1}
		(a) Pareto fronts for ex-1 through ex-4 at $s_1$.
		%\caption{(a) Pareto fronts at $s_1$.}
		%\label{expareto1}
		\vspace{2em}
	\end{minipage}
	\begin{minipage}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/ex-pareto2}
		(b) Pareto fronts for ex-1 through ex-4 at $s_2$.
		%\caption{(b) Pareto fronts at $s_2$.}
		%\label{expareto2}
	\end{minipage}
	\caption{Comparison of Pareto fronts for initial optimization experiments, ex-1 through ex-4.}
	\label{expareto}
\end{figure}

@@

Equations (\ref{eq:awa:firstconstr}) to
(\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
laser radius, gun phase, and linac cavity phases (in that order). 
These are parameters in the simulation 
that must be defined, but do not vary during the optimization.
%\vspace{-1em}
The AWA 
design variables, objectives, and constraints in the OPAL input file as shown in
the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}). 
%\vspace{0.2cm}
\begin{samepage}
	\begin{Verbatim}[fontsize=\scriptsize]

@@

	OPTIMIZE, INPUT="tmpl/optLinac-40nC.tmpl",
	OUTPUT="optLinac-40nC",
	OUTDIR="results",
	OBJECTIVES = {rmss3, rmsx3, rmsy3, rmspx3, rmspy3, de3},
	DVARS = {dv0, dv1, dv4, dv5, dv6, dv7},
	CONSTRAINTS = {c1, c2, c3},
	INITIALPOPULATION=656,
	MAXGENERATIONS=200,
	NUM_MASTERS=1,
	NUM_COWORKERS=8,
	SIMTMPDIR="tmp",
	TEMPLATEDIR="tmpl",
	FIELDMAPDIR="fieldmaps",
	NUM_IND_GEN=328,
	GENE_MUTATION_PROBABILITY=0.01,
	MUTATION_PROBABILITY=0.01,
	RECOMBINATION_PROBABILITY=0.09;
	QUIT;
	\end{Verbatim}
\end{samepage}

>>>>

\iffalse
%\vspace{0.2cm}
\begin{samepage}
	\begin{Verbatim}[fontsize=\scriptsize]
	OPTION, ECHO=FALSE;
	OPTION, INFO=TRUE;

@@

	OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
	OUTPUT="optLinac_40nC",
	OUTDIR="results",
	OBJECTIVES = {rmss1, emitx1, rmss2, emitx2},
	DVARS = {dv0, dv1, dv2, dv3, dv4, dv5, dv6, dv7},
	CONSTRAINTS = {c1, c2},
	INITIALPOPULATION=80,
	MAXGENERATIONS=100,
	NUM_MASTERS=1,
	NUM_COWORKERS=8,
	SIMTMPDIR="tmp",
	TEMPLATEDIR="tmpl",
	\end{Verbatim}
\end{samepage}
\fi
%\vspace{0.2cm}

@@

\begin{figure}
	\centering
	\begin{minipage}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/ex-pareto1-paperedit}
		(a) Pareto fronts for ex-1 through ex-4 at $s_1$.
		%\caption{(a) Pareto fronts at $s_1$.}
		%\label{expareto1}
		%\vspace{2em}
	\end{minipage}
	\begin{minipage}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{figures/ex-pareto2-paperedit}
		(b) Pareto fronts for ex-1 through ex-4 at $s_2$.
		%\caption{(b) Pareto fronts at $s_2$.}
		%\label{expareto2}
	\end{minipage}
	\caption{Comparison of Pareto fronts for initial optimization experiments, ex-1 through ex-4.}
	\label{expareto}
\end{figure}

@@

Equations (\ref{eq:awa:firstconstr}) to
(\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
laser radius, gun phase, and linac cavity phases (in that order). 
These are parameters in the simulation 
that must be defined, but do not vary during the optimization.
%\vspace{-1em}
The AWA 
design variables, objectives, and constraints in the OPAL input file as shown in
the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}). 
%\vspace{0.2cm}
\iffalse
\begin{samepage}
	\begin{Verbatim}[fontsize=\scriptsize]

@@

	OPTIMIZE, INPUT="tmpl/optLinac-40nC.tmpl",
	OUTPUT="optLinac-40nC",
	OUTDIR="results",
	OBJECTIVES = {rmss3, rmsx3, rmsy3, rmspx3, rmspy3, de3},
	DVARS = {dv0, dv1, dv4, dv5, dv6, dv7},
	CONSTRAINTS = {c1, c2, c3},
	INITIALPOPULATION=656,
	MAXGENERATIONS=200,
	NUM_MASTERS=1,
	NUM_COWORKERS=8,
	SIMTMPDIR="tmp",
	TEMPLATEDIR="tmpl",
	FIELDMAPDIR="fieldmaps",
	NUM_IND_GEN=328,
	GENE_MUTATION_PROBABILITY=0.01,
	MUTATION_PROBABILITY=0.01,
	RECOMBINATION_PROBABILITY=0.09;
	QUIT;
	\end{Verbatim}
\end{samepage}
\fi
